Light inextensible strings (thread) under tension in the Schwarzschild geometry

### 2021-01-26 physics_educator_rebuttal.txt

> The paper has imprecise usage of GR terminology. A few statements are
> unclear. Examples include:
>  
> 1.  "straight line" in the vicinity of black
> hole... (Introduction/paragraph 1) I believe it refers to straight
> line in spatial sections of black hole.
>

The original sentence was:

:: The sentence was: Here I show how considering light inextensible 
:: string can be used to interpret the concept of "straight line" in the
:: vicinity of a black hole.

It might be rephrased: "...interpret the concept of "straight line" in
spatial sections of a black hole", but I believe this form of words
would be potentially misleading.  My thinking was that the concept of
"straight line" ---in the abstract---is to be re-interpreted in the
manuscript as the path taken by a light inextensible string.

It now reads "Here I interpret a straight line as the path adopted by
a stationary, light inexensible string under tension passing between
two points"

There is a little bit of repetition in the revised manuscript, but I
think it is worth it for the extra clarity.

### 2021-01-26 string_physics_educator_revision2.tex
fixes #24

General relativity is a topic of long-standing fascination for physics
undergraduates~\cite{christensen2012}.  Students appreciate everyday
illustrations of the concepts involved, as recent educational work on
gravitational wave visualisations attests~\cite{overduin2018}.  Here I
show how considering light inextensible string can be used to
interpret the concept of ``straight line'' in the vicinity of a black
hole.  The analysis presented here would be suitable for an
undergraduate homework problem~\cite{romano2019}.

A light string's being under tension means that its path will be an
extremum of proper length: non-extremal paths between two fixed points
cannot be in stable equilibrium as the tension acts to shorten the
path; stable paths must therefore be of extremal proper-length.
In flat space, the calculus of variations
proves that the path is straight in the sense of zero curvature.  In
terrestrial gravity, standard $25\times
10^{-6}\unit{kg}\cdot\unit{m}^{-1}$ cotton sewing thread at its
breaking strain of about $40\unit{N}$ would have a sag of~${\sim}
6\times 10^{-6}\unit{m}$ over a $1\unit{m}$ horizontal scale: barely
perceptible.  How does such a quotidian observation translate into the
vicinity of a black hole?  Would the ``warping of space'' result in
{\em visibly} curved thread?

>>>>

General relativity is a topic of long-standing fascination for physics
undergraduates~\cite{christensen2012}.  Students appreciate everyday
illustrations of the concepts involved, as recent educational work on
gravitational wave visualisations attests~\cite{overduin2018}.  Here I
interpret a straight line as the path adopted by a stationary, light
inexensible string under tension passing between two points.  The
analysis presented here would be suitable for an undergraduate
homework problem~\cite{romano2019}.

Considering only stationary spacetimes, we define the proper length of
a string to be the result of integrating the spatial part of the
metric tensor along string's path between its endpoints.  A light
string's being under tension means that its path will be an extremum
of proper length: non-extremal paths between two fixed points cannot
be in stable equilibrium as the tension acts to shorten the path;
stable paths must therefore be of extremal proper-length.  In flat
space, the calculus of variations proves that the path is straight in
the sense of zero curvature.  In terrestrial gravity, standard
$25\times 10^{-6}\unit{kg}\cdot\unit{m}^{-1}$ cotton sewing thread at
its breaking strain of about $40\unit{N}$ would have a sag of~${\sim}
6\times 10^{-6}\unit{m}$ over a $1\unit{m}$ horizontal scale: barely
perceptible.  How does such a quotidian observation translate into the
vicinity of a black hole?  Would the ``warping of space'' result in
{\em visibly} curved thread?
